---
title: "Dissatisfied customers"
author: "Siddharth Patil"
date: "May 13, 2018"
output:
  word_document: default
  html_document: default
---
#Import the training dataset
```{r}
data = read.csv("train.csv", header = T)
#data$TARGET = as.factor(data$TARGET)
plot(as.factor(data$TARGET)) #Balancing the dataset is required
```

#Balancing the dataset
```{r}
#oversampling the minority class and undersampling the majority class
library(ROSE)
data = ovun.sample(TARGET ~ ., data = data, method = "both",N = 76020)$data
data$TARGET = as.factor(data$TARGET)
#plot(data$TARGET) #plot indicates that balancing is done #The dataset is balanced
```

#Data normalization
```{r}
# normalize <- function(x) {
#  return ((x - min(x)) / (max(x) - min(x))) }
#  
# data_norm = as.data.frame(lapply(data, normalize))
# 
# data_norm$TARGET = as.factor(data$TARGET)
```

#Divide the data set into test and train datasets
```{r}
## 75% of the sample size
smp_size = floor(0.75 * nrow(data))

## set the seed to make your partition reproducible
set.seed(123)
train_ind = sample(seq_len(nrow(data)), size = smp_size)

train_data = data[train_ind, ]
test_data = data[-train_ind, ]
```

#Variable selection
```{r}
# log_reg = glm(TARGET ~ ., data, family = "binomial")
# 
# library(broom)
# tm = tidy(log_reg) #data frame with model summary parameters as columns
# 
# # get variables with p value less than 0.05
# library(dplyr)
# sign_variables = tm$term[tm$p.value < 0.05] %>% paste(collapse = " + ")
# sign_variables = paste0('TARGET', ' ~ ', sign_variables)
# sign_variables
```

#Building a model using naive Bayes
```{r}
library(e1071)
NB = naiveBayes(TARGET ~ .,train_data)
```

# Use the model to make predictions for the test data set
```{r}
test_predictions = predict(NB, newdata = test_data)
```

#Model diagnostics
```{r}
#Confusion matrix
library(caret)
confusionMatrix(table(test_data$TARGET, test_predictions))

#ROC curve
roc.curve(test_data$TARGET, test_predictions)